\LARGE \bf Steering a Swarm Using Global Inputs\\ and Swarm Statistics

### 2017-10-03 journalSwarmControl/Reviews/Response.tex

		\includegraphics[width=8cm]{engineeringLogo.eps}

		\begin{flushright}
		Aaron T.\ Becker\\Department of Electrical Engineering\\University of Houston\\Houston, TX 77004, USA\\Email: atbecker@central.uh.edu\\Web: youTube.com/aabecker5\\

		\today \vspace{2cm} \\
		\end{flushright}

		#1\medskip\\ 
		\medskip\\
		Dear #2 Editorial Office,\medskip\\
		Please find attached the revised paper, #1,
		along with the document containing a response to the reviewers. We are grateful to the reviewers for helping us improve our manuscript through their comments and questions. Please let us know if further information is required.\medskip\\

@@

\response{The paper deals with an interesting problem for the community and it is
very well written. Some improvements may be achieved following
reviewers comments in providing more insights or details on several
aspects. For example, as reported by Reviewer 3, simulation scenarios
could be of higher complexity with respect to the shown experiments so
to prove other potentialities of the proposed approach. In addition to the corrections requested by reviewers I suggest also
the following:}

 To illustrate the flexibility of the algorithm we tested two additional workspaces, \emph{{\sffamily E}-shaped} and  \emph{Spiral}, without changing the algorithm. 
 More complicated workspaces could be generated by composing these workspaces. See Figs. 16 and 17.

\response{- Simplify equation 3 removing dots and reporting $A^3 B$ instead of
$A^{n-1}B$ since the dimension of the system is 4. Moreover, variable $n$
is later used as the number of robots in the swarm.}
This has been changed.

\response{- In Section V would avoid the subdivision in subsections since they
are very short and in this case the subdivision does not help the flow
of reading.}
Quite right.  We changed these subdivisions to be inline paragraph headings.

@@

	\Reviewer{\#2}No comments were submitted from Reviewer 2.

	\Reviewer{\#3}\response{In the paper the terms: micro, nano robots, and particles are used interchangeably, that is perfectly fine, however, it would be better in the very beginning to make that clear possible with a footnote, especially the use of the term particles. }

	Good point. We have edited the paper so that references to micro and nano robots are only in the introduction, related work, and conclusion. We have replaced 
	``robot'' with ``particle'' unless the object to be controlled is a hardware robot (such as a kilobot).
	Additionally, in paragraph 1 we now state ``Instead, this paper treats the robots as particles that are steered by a global control signal broadcast to the entire population."

	\response{In page two, column 1, the authors state that "process noise cancels the differentiating effects... tens of robots." The term tens of robots is not clear. It would also help a citation if it exists.}
	This has been clarified by modifying text and adding references:
	``Similarly, our previous work focused on exploiting inhomogeneity between robots [16], [17]. These control algorithms theoretically apply to any number of robots, even robotic continuums. However, all these works never controlled more than twelve robots at a time because process noise cancels the differentiating effects of robot inhomogeneity. We desire control algorithms that extend to many thousands of robots.''

### 2017-10-03 journalSwarmControl/experiment.tex
updated the capitalization value iteration

To solve both these problems, this paper models object movement as a Markov Decision Process (MDP) with non-deterministic movement.  
  Value Iteration is used to learn an \emph{optimal policy}~\cite{Thrun2005}.
   At each state the object can be commanded to move in one of eight directions with a small probability of moving in a wrong direction.

@@

$\mathbf{M}_{\rm{BFS}}$ and the value function are shown in Fig.~\ref{fig:BFSGradient}. 
In 10 simulations with 100 particles, pushing the object to goal using BFS required 183$\pm$179 s while Value Iteration required 90$\pm$35 s (mean$\pm$std).
%\todo{(report results of 10 simulations with BFS and with PI.  Give mean and std)}

@@

\begin{figure}\begin{center}\begin{overpic}[width=0.4\columnwidth]{MDPEmaze.pdf}\end{overpic}~\begin{overpic}[width=0.4\columnwidth]{EmazeFinal.pdf}\end{overpic}\\
\vspace{.25em}
\begin{overpic}[width=0.4\columnwidth]{Spiral.pdf}\end{overpic}~\begin{overpic}[width=0.4\columnwidth]{SpiralSuccess.pdf}\end{overpic}
\end{center}
\caption{\label{fig:Emaze} We tested three workspaces. The control policies from Value Iteration for an {\sffamily E}-shaped and a spiral workspace are shown in the left column.
}
\end{figure}
\begin{figure}
\centering
\begin{overpic}[width=.5\columnwidth]{DifferentShapes.pdf}\end{overpic}
\vspace{-1em}
\caption{\label{fig:DifferentMazes} Completion times for three workspaces.}
\end{figure}

>>>>

To solve both these problems, this paper models object movement as a Markov Decision Process (MDP) with non-deterministic movement.  
  Value iteration is used to learn an \emph{optimal policy}~\cite{Thrun2005}.
   At each state the object can be commanded to move in one of eight directions with a small probability of moving in a wrong direction.

@@

$\mathbf{M}_{\rm{BFS}}$ and the value function are shown in Fig.~\ref{fig:BFSGradient}. 
In 10 simulations with 100 particles, pushing the object to goal using BFS required 183$\pm$179 s while value iteration required 90$\pm$35 s (mean$\pm$std).
%\todo{(report results of 10 simulations with BFS and with PI.  Give mean and std)}

@@

\begin{figure}\begin{center}\begin{overpic}[width=0.4\columnwidth]{MDPEmaze.pdf}\end{overpic}~\begin{overpic}[width=0.4\columnwidth]{EmazeFinal.pdf}\end{overpic}\\
\vspace{.25em}
\begin{overpic}[width=0.4\columnwidth]{Spiral.pdf}\end{overpic}~\begin{overpic}[width=0.4\columnwidth]{SpiralSuccess.pdf}\end{overpic}
\end{center}
\caption{\label{fig:Emaze} We tested three workspaces. The control policies from value iteration for an {\sffamily E}-shaped and a spiral workspace are shown in the left column.
}
\end{figure}
\begin{figure}
\centering
\begin{overpic}[width=.5\columnwidth]{DifferentShapes.pdf}\end{overpic}
\vspace{-1em}
\caption{\label{fig:DifferentMazes} Completion times for three workspaces.}
\end{figure}
